### 2018-06-14 papers/synth/intro.tex
reference fix
intro fixed

%Motivate VTS
Eukaryotic cells, including human cells, consist of multiple membrane-bound compartments.
%
Material is transported among these compartments by the vesicle
transport system (VTS).
%
Briefly, the source compartment produces a membrane-bound packet of
molecules called a vesicle.
%
After release, this vesicle specifically recognizes the correct target
compartment within the cell, and fuses with it.
%
A lot of information about the molecules that form the machinery of
the VTS has been discovered, including their regulatory interaction
with each other. 
% %
% \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
%
In spite of this detailed knowledge at the level of the molecules, the
structure of the VTS network, or the road-map of the eukaryotic cell,
is far from complete.
%
The current knowledge of the network is put together from a patchwork
of biological experiments and is scattered across several publications.
%
Even after this information is collected and put together, we find
that the network obtained is still not complete; new vesicles and new
contents in previously known vesicles are constantly being discovered.
%
The synthesis for the unknown pieces may be assisted by computation on
the graph model of VTSs.
%
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at Appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arising from the VTSs.

We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
%
Please look at appendix~\ref{sec: model}
for a detailed discussion on pros and cons of the model.
% Describe VTS in detail

@@

% Partial info defence
%
As we have discussed earlier, our understanding of VTSs is partial.
%
% It largely means that the current knowledge is due to the patchwork
% of biological experiments~\cite{model} for identifying the compartments,
% channels, molecules, and their activity and regulatory control.
% %
% Often the information is scattered around in several publications.
% %
% Even after with some effort we may collate all the known information about
% a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
%For example, it is possible that some edges may not have been
%discovered in a VTS that does not satisfy the stability condition.
% nature of missing information has already been elaborated upon in the first paragraph
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do
synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into one of satisfiability of
quantified Boolean formulas(QBFs). 
%

>>>>

%Motivate VTS
Eukaryotic cells, including human cells, consist of multiple membrane-bound compartments.
%
Material is transported among these compartments by the vesicle
transport system (VTS).
%
Briefly, the source compartment produces a membrane-bound packet of
molecules called a vesicle.
%
After release, this vesicle specifically recognizes the correct target
compartment within the cell, and fuses with it~\cite{alberts2013essential}.
%
A lot of information about the molecules that form the machinery of
the VTS has been discovered, including their regulatory interaction
with each other~\cite{bonifacino2004mechanisms}. 
% %
% \todo{connect to function }{We also know a lot about the specific functions} of these molecules and how these molecules interact amongst each other.
%
In spite of this detailed knowledge at the level of the molecules, the
structure of the VTS network, or the road-map of the eukaryotic cell,
is far from complete.
%
For example, although thee localization of various SNAREs in the cell is known, and also their site of action~\cite{hong2014tethering}, for most SNAREs, how they first reached the compartments they reside in is not known.
%
The current knowledge of the network is put together from a patchwork
of biological experiments and is scattered across several publications.
%
Even after this information is collected and put together, we find
that the network obtained is still not complete; new vesicles and new
contents in previously known vesicles are constantly being discovered(some new discoveries include~\cite{chanaday2017you, d2017tethering, rodepeter2017indication, zhao2017conserved}).
%
The synthesis for the unknown pieces may be assisted by computation on
the graph model of VTSs.
%
% 
%In this work, we use a model described in [] to find out, given a partial
%VTS graph and details about interactions amongst its molecules, what the complete graph of the
%VTS could look like. (Please look at Appendix A for the detailed discussion on pros and cons of the
%model.
%
%Eukaryotic cells, including human cells, consists of multiple compartments.
%
%Vesicle Traffic Systems(VTSs) are the material transport mechanisms among the compartments inside the cells~\cite{vtsIntro}.
%
%Almost all subsystems of the cells depend on VTSs.
%
%Therefore, understanding how VTSs functions is one of the key
%questions of cell biology.
%
In this paper, we are looking at the computational questions 
arising from the VTSs.

%
In particular, the VTS molecules to keep in mind for the purpose of this paper are SNARE proteins. SNAREs drive the recognition of the target compartment by vesicles and their subsequent fusion. Functionally, SNAREs can be divided into v-SNAREs (which are present on vesicles) and t-SNAREs (which are present on compartments). A vesicle fuses with a compartment if its v-SNARE can form a complex with the t-SNARE present on that compartment. Not all v- and t- SNARE combinations can form complexes; this constraint forms part of the basis for the specificity of vesicle traffic~\cite{jahn2006snares}. The activity of SNARE proteins is further regulated by their interaction with other traffic molecules, such as SM proteins~\cite{sudhof2009membrane} and proteins of tethering complexes~\cite{hong2014tethering}.
%
We use the model of VTSs that has been presented in~\cite{shukla2017discovering}.
%
Please look at appendix~\ref{sec:model}
for a detailed discussion on pros and cons of the model.
% Describe VTS in detail

@@

% Partial info defence
%
As we have discussed earlier, our understanding of VTSs is partial.
%
% It largely means that the current knowledge is due to the patchwork
% of biological experiments~\cite{model} for identifying the compartments,
% channels, molecules, and their activity and regulatory control.
% %
% Often the information is scattered around in several publications.
% %
% Even after with some effort we may collate all the known information about
% a VTS, we may still have unknown pieces of the system; new vesicles and new contents in previously known vesicles are constantly being discovered.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
%For example, it is possible that some edges may not have been
%discovered in a VTS that does not satisfy the stability condition.
% nature of missing information has already been elaborated upon in the first paragraph
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, and learning activity functions.
%
We also consider variation on the properties against which we do
synthesis, namely stability, and $k$-connectedness that states that the VTS remains connected after removing any $k-1$ edges.
%
We have assumed that the given partial VTS is always well-fused whereas properties like stability and k-connectedness may not hold in the partial VTS.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into one of satisfiability of
quantified Boolean formulas(QBFs). 
%
